KV Analysis for Non-Expressive performances

### 2020-05-12 material/analysis/stim_n/duration.Rmd
change file location / file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```

# Duration Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

>>>>

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

# Duration Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

### 2020-05-12 material/analysis/stim_n/ioi_onset.Rmd
change file location / file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
## Individual
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

## Exclude outlier participants
```{r cv_outlier, echo = FALSE}
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```

>>>>

### Valid performances (exclude outliers)
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```
- The number of excluded performance: `r ioi_all$N-nrow(excluded_ioi)`

# IOI Variability
## 1. All - individual
- Average CV for each participant

```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
## 2. All - group
- Average CV

```{r cv_all, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
```

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

```{r export, include = FALSE}
fwrite(excluded_cv, "./onset_valid.csv")
```

### 2020-05-12 material/analysis/stim_n/kv.Rmd
change file location / file path
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Analysis for Non-Expressive performances (Key Velocity)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---
_
Description: This is a rough overview of non-expressive performance from teaching-v2.0 (KV).

@@

### Exclude outlier performances
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```

>>>>

---
title: 'KV Analysis for Non-Expressive performances'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

Description: This is a rough overview of non-expressive performance (KV) from teaching-v2.0.

@@

## 2. All - group
- Average CV

```{r cv_all, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
```

### Valid performances (exclude outliers)
```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

```{r export, include = FALSE}
fwrite(excluded_cv, "./kv_valid.csv")
```
